### 2019-09-07 manuscript/manuscript.tex
edited disco

We re-analyzed three published temporal genomic datasets and detected the
genome-wide signature of linked selection acting over tens of generations.
Furthermore, we find the dynamics of temporal autocovariance are consistent
with theory; as linkage disequilibria and additive variation for fitness decay
through time, temporal covariance decays. In reanalyzing one study
\parencite{Barghi2019-qy}, we find that after sixty generations, greater than
20\% of the variation in allele frequency change is directly due to the action
linked selection. Capitalizing on replicated evolve-and-resequence study
designs, we characterized the extent to which convergent selection pressures
lead to parallel changes in allele frequency across replicate populations,
finding that the correlation in allele frequency changes varies from 0.1 (in
the \cite{Barghi2019-qy} study) to 0.36 (in the \cite{Kelly2019-dc} study).

@@

One limitation of our current work here is that none of the studies we
re-analyzed had linkage disequilibria data for the evolved populations. Our
theory of temporal autocovariance tells us that the temporal autocovariances a
neutral site experiences is determined by the product of the expected linkage
disequilibrium and additive fitness variation that persists through the
generations. This leads to a clear prediction: regions of higher linkage
disequilibrium and lower recombination should have greater temporal
autocovariance than regions with lower LD and higher recombination.
Unfortunately, we lack a high-resolution recombination map for \emph{D.
simulans} and while there are LD data for \emph{D. simulans}
\parencite{Signor2018-wg} we did not find a relationship between temporal
covariance and LD.

@@

Finally, in re-analyzing the \textcite{Barghi2019-qy} study, we find evidence
of linked selection dynamics more complex than expected under a model of
directional selection occurring until fitness variation is exhausted. This is
due either to a change in the environment and its consequences for the fitness
of regions in the genome, recombination breaking up selected alleles, or
epistatic interactions between loci. It is important to note that the original
study did not intentionally alter the environment in any way; this signal is
attained without intentionally seeking it out. Discerning which of these is
creating negative temporal autocovariance is a sizable challenge, requiring
sequencing each generation and LD data.

Overall, we hope this will encourage more temporal genomic studies in both
laboratory and natural populations. Understanding the dynamics of linked
selection over short timescales can help us finally unite phenotypic studies of
rapid adaptation of polygenic adaptations with a detectable genomic signature,
to address long-standing questions on linked selection, evolutionary
quantitative genetics, and the overall impact selection has on genetic
variation.

>>>>

We re-analyzed three published temporal genomic datasets and detected the
genome-wide signature of linked selection acting over tens of generations.
Furthermore, we find the dynamics of temporal autocovariance are consistent
with theory; \gc{the temporal covariance in allele frequencies decay}
as \gc{presumably due to the} linkage disequilibria and additive variation \gc{for
fitness present in a particular generation} decay through time \graham{So we need to be careful here. As
  the additive var for fitness may be constant. It's that the VA from
  a particular gen is decaying. Not sure if }. In reanalyzing one study
\parencite{Barghi2019-qy}, we find that after sixty generations, greater than
20\% of the variation in allele frequency change is directly due to the action
linked selection. Capitalizing on replicated evolve-and-resequence study
designs, we characterized the extent to which convergent selection pressures
lead to parallel changes in allele frequency across replicate populations,
finding that the correlation in allele frequency changes varies from 0.1 (in
the \cite{Barghi2019-qy} study) to 0.36 (in the \cite{Kelly2019-dc}
study). \graham{Are these just repeat numbers from main text? If so
  nix this sentence}

@@

One limitation of our current work here is that none of the studies we
re-analyzed had linkage disequilibria data for the evolved populations. Our
theory of temporal autocovariance tells us that the temporal autocovariances a
neutral site experiences is determined by the product of the expected linkage
disequilibrium and additive fitness variation that persists through the
generations \gc{ \parencite{Buffalo}}. This leads to a clear prediction: regions of higher linkage
disequilibrium and lower recombination should have greater temporal
autocovariance than regions with lower LD and higher recombination.
Unfortunately, we lack a high-resolution recombination map for \emph{D.
simulans} and while there are LD data for \emph{D. simulans}
\parencite{Signor2018-wg} we did not find a relationship between temporal
covariance and LD. \graham{Is important point. We'll likely need plots for supp}

@@

%more complex than expected under a model of
%directional selection occurring until fitness variation is exhausted

Finally, in re-analyzing the \textcite{Barghi2019-qy} study, we find evidence
of \gc{complex} linked selection dynamics. This is
due either to a change in the environment and its consequences for the fitness
of regions in the genome, recombination breaking up selected alleles, or
epistatic interactions between loci. It is important to note that the original
study did not intentionally alter the environment in any way; this signal is
attained without intentionally seeking it out. Discerning which of these is
creating negative temporal autocovariance is a sizable challenge, requiring
sequencing each generation and LD data.

%help us finally

Overall, we hope this will encourage more temporal genomic studies in both
laboratory and natural populations. Understanding the dynamics of linked
selection over short timescales \gc{will help to} unite phenotypic studies of
rapid adaptation of polygenic adaptations with a detectable genomic signature,
to address long-standing questions on linked selection, evolutionary
quantitative genetics, and the overall impact selection has on genetic
variation.
